Investigating Cross-Sectional Size Distribution of Randomly Distributed 3D Spheres

### 2020-05-24 Paper/main.tex
Fixed typos

Mathematically, determining the distribution of spherical particles from planar
sections is a well known problem called Wicksell's Corpuscle Problem
\cite{DWicksell}, named after S. D. Wicksell, who solved the problem in 1925. With
this solution, it is possible to determine the original distribution of
spherical particles. Thus, it is possible to determmine the distribution of
particle sizes in a solid from its observed cross-section, allowing us to
identify and classify materials better \cite{Cuzzi2016}.

@@

If we compute the integral in Equation~\ref{eq:phi_OG}, replacing $f(R)$ with
$\delta(R-R_0)$ we find:
\begin{equation}
\phi(x) = \int_{x}^{\infty}\frac{x\delta(R-R_0)}{\sqrt{R^2 - x^2}} =
\frac{xH(R_0-x)}{\sqrt{R_0^2-x^2}}
\label{eq:phi_constant}
\end{equation}
where $H(R_0 - x)$ is the heaviside function, which ``turns on'' the
distribution only for $x < R0$ as it is not possible to have a circular radius
$x$ larger than the spherical radius. So we aim to see our experimental data
reproduce this distribution \cite{Kong2005}. We also investigated how changing the
value of $R_0$ affects the experimental distribution.

>>>>

Mathematically, determining the distribution of spherical particles from planar
sections is a well known problem called Wicksell's Corpuscle Problem
\cite{DWicksell}, named after S. D. Wicksell, who solved the problem in 1925. With
this solution, it is possible to determine the original distribution of
spherical particles. Thus, it is possible to determine the distribution of
particle sizes in a solid from its observed cross-section, allowing us to
identify and classify materials better \cite{Cuzzi2016}.

@@

If we compute the integral in Equation~\ref{eq:phi_OG}, replacing $f(R)$ with
$\delta(R-R_0)$ we find:
\begin{equation}
\phi(x) = \int_{x}^{\infty}\frac{x\delta(R-R_0)}{\sqrt{R^2 - x^2}} =
\frac{xH(R_0-x)}{\sqrt{R_0^2-x^2}}
\label{eq:phi_constant}
\end{equation}
where $H(R_0 - x)$ is the Heaviside function, which ``turns on'' the
distribution only for $x < R0$ as it is not possible to have a circular radius
$x$ larger than the spherical radius. So we aim to see our experimental data
reproduce this distribution \cite{Kong2005}. We also investigated how changing the
value of $R_0$ affects the experimental distribution.
